Growing libraries of concepts with wake-sleep program induction

### 2018-07-22 talk.tex
vision slide

@@

\begin{frame}{Contributions}

@@

  \textbf{Future work}

  \begin{itemize}
  \item More human-like learning: intelligently composing new tasks, 
    \pause
  \item Theory learning
    \item Planning
    \end{itemize}

>>>>

  \vfill
  \only<1>{
  Recognition model: Neural net.\\
  Red: Bottom-up inference.\\
  Gray: Observed.\\
  White: Latent.\\
  Boxed (plate): Repeated.\\
  }
  \only<2>{
  \begin{tikzpicture}[xscale=1.25,line width=1mm]
    \node at (0,0) (d){DSL};
    \node at ([yshift = -2cm]d) (t){$\text{Task}$};

    \node at ([xshift = 2cm]t) (nn){
      \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.3,shift={+(-1,2.5)}}]
       \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
        \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
        \node[rectangle] at (1,1) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (I-\name) at (0,-\y) {};
        \foreach \name / \y in {1,...,3}
            \node[neuron] (H-\name) at (1,-\y-0.5) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (O-\name) at (2,-\y) {};
        \foreach \source in {1,...,4}
            \foreach \dest in {1,...,3}
                \draw [-latex] (I-\source) -- (H-\dest);
        \foreach \source in {1,...,3}
            \foreach \dest in {1,...,4}
                \draw [-latex] (H-\source) -- (O-\dest);
      \end{tikzpicture}
    };
    \node[align = center, text width = 1cm] at ([yshift = 0.7cm]nn.north) {\baselineskip=0pt \Small Recog. model\par};
    \draw [->] (t.east) -- ([xshift = -0.5cm]nn.west);

    \node[draw,rounded corners, inner sep = 10] at ([xshift = 4.2cm,yshift = -1cm]) (s){Search};
%    \node at ([xshift=-7pt,yshift=5pt]s.north west) {$\mathcal{D}$};

    \draw [->] ([xshift = 0.5cm]nn.east) -- ([yshift = -0.25cm]s.west);
    \draw [->,rounded corners] (d.east) -- ([yshift = 2cm]nn.center) -- ([yshift = 0.25cm]s.west);

    \node[align=left] at (7,-1) (f) {Programs};
    \draw [->  ] (s.east) -- (f.west);

    \draw [->  ,rounded corners] (t.south) -- ([yshift = -0.5cm]t.south) -- ([yshift = -0.5cm] s.south |- t.south) -- (s.south);
  \end{tikzpicture}}
  %% Recognition model: Neural net.\\
  %% Red: Bottom-up inference.\\
  %% Gray: Observed.\\
  %% White: Latent.\\
  %% Boxed (plate): Repeated.\\

@@

\begin{frame}{Vision}

@@

  %% \textbf{Future work}

  %% \begin{itemize}
  %%   \pause
  %% \item Theory learning
  %%   \item Planning
  %%   \end{itemize}
